Untitled

### 2021-03-13 ms/manuscript.Rmd
Update MS
- fix various little things

---
title: ""
bibliography: 
  - references.bib
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 12pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes # for converting tex to doc
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-plant-research.csl"]
    includes:
      in_header: journal-of-plant-research.sty
# Prevent figures from moving around, suppress automatic "Figure #:" in captions
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
  \renewcommand{\caption}{}
params:
  output_type: "ms"
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

**Corresponding author**  
Joel H. Nitta  
Department of Integrated Biosciences, Graduate School of Frontier Sciences, The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8562, Japan  
Phone: +81-81-4-7136-3681  
Fax: +81-4-7136-3680  
email: joelnitta\@gmail.com

@@

@@

\*\*\* NOTE TO REVIEWERS: The DOI for the dataset will not be active until the paper is accepted. Until then, this link can be used for the dataset https://figshare.com/s/d6349abf01a3756a5aae  \*\*\*

@@

Relative humidity in the growth chambers was high when samples were first inserted, then gradually decreased to the target value maintained by each drying salt (`r s_figure("chamber")`).
In a few cases (particularly species with larger fronds, \eg, *C. apiifolia*), the NaCl chamber did not reach equilibrium humidity before 2 d (`r s_figure("chamber")`).
Brief fluctuations in humidity were observed when chambers were opened to insert or remove samples (`r s_figure("chamber-s")`).

>>>>

---
title: ""
bibliography: 
  - references.bib
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 12pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes # for converting tex to doc
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-plant-research.csl"]
    includes:
      in_header: journal-of-plant-research.sty
# Prevent figures from moving around, suppress automatic "Figure #:" in captions
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
  \renewcommand{\caption}{}
params:
  output_type: "ms"
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

```{r first-page, results = "asis", eval = params$output_type == "ms", purl = FALSE}
cat("
**Corresponding author**  
Joel H. Nitta  
Department of Integrated Biosciences, Graduate School of Frontier Sciences, The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8562, Japan  
Phone: +81-4-7136-3681  
Fax: +81-4-7136-3680  
email: joelnitta\\@gmail.com

@@

\\newpage
")
```

@@

\*\*\* NOTE TO READER: The DOI for the dataset will not be active until the paper is accepted. Until then, this link can be used for the dataset https://figshare.com/s/d6349abf01a3756a5aae  \*\*\*

@@

Relative humidity in the growth chambers was high when samples were first inserted, then gradually decreased to the target value maintained by each drying salt (`r s_figure("chamber")`).
In a few cases (particularly species with larger fronds, \eg, *C. apiifolia*), the NaCl chamber did not reach equilibrium humidity before 2 d (`r s_figure("chamber")`).
Brief fluctuations in humidity were observed when chambers were opened to insert or remove samples (`r s_figure("chamber")`).
